D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-27 ootavacuous.tex
Add executable formal hardware memory-model citations
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The C++ standard imposes many constraints, and these have been considered
in prior work.
In real-world C++ implementations, the standard's
abstract machine must be mapped onto real hardware, however, and
this mapping has not been considered to any significant degree.
It imposes additional constraints stemming from hardware architecture and
design,
which have been only partially accounted for in the standard and other work.
Part of the reason for this is
that accurate and executable formal descriptions of hardware memory
models did not appear until after the standard was released.
But they do exist now.

>>>>

The C++ standard imposes many constraints, and these have been considered
in prior work.
In real-world C++ implementations, the standard's
abstract machine must be mapped onto real hardware, however, and
this mapping has not been considered to any significant degree.
It imposes additional constraints stemming from hardware architecture and
design,
which have been only partially accounted for in the standard and other work.
Part of the reason for this is
that accurate and executable formal descriptions of hardware memory
models did not appear until after the standard was
released~\cite{JadeAlglave2011ppcmem,Maranget2012TutorialARMPower}.
But they do exist now.
